Fast Sorting on Modern Computers

### 2005-07-18 docs/tech_report/quick.tex
updated the scripts in the docs directory. removed a debug line. updated the data file. made small fixes to quick.tex

Each of the \code{while} loops in \code{partition} is a branch, and each
iteration of that loop corresponds to that branch being taken, while each
exchange corresponds to that branch being not-taken. So the fewer

>>>>

Each of the \cc{while} loops in \cc{partition} is a branch, and each
iteration of that loop corresponds to that branch being taken, while each
exchange corresponds to that branch being not-taken. So the fewer
